Risks of Running Vulnerable Container Images for Data Analysis on HPC Clusters

### 2019-11-12 paper.tex
results section

Containers, which provide operating system (OS) level virtualization, are very
popular. This is because they are very lightweight, flexible, resource-efficient,
provide fast development cycles, continuous delivery,
and cost reduction of infrastructure. OS-level virtualization gained a lot of interest when Docker was
introduced in 2013~\cite{gantikow2016providing}. However, Docker has security concerns due to which it
is not supported by High Performance
Computing (HPC) environments. As a result, Singularity came in 2016 with the goal of providing support
for HPC environments. It is used in many clusters including Compute Canada.
Table \ref{fig:cluster_list} illustrates the reported usage of Singularity on HPC clusters~\cite{kurtzer2017singularity}.

@@

No doubt containers have gained a lot of popularity, however containers tightly
integrate with the host due to the sharing of the kernel, 
mounted file systems, and devices, which raises security
concerns. Figure \ref{fig:container-overview} provides overview of the containers architecture.
They also share three main security threats with other virtualization
techniques~\cite{gantikow2016providing}.

@@

To answer that question, we scan all images that are used on Compute
Canada clusters by neuroscience field. Scanning refers to the practice of
collecting all information about the container image, investigating it
for vulnerabilities, and finally producing a
report to summarize scanning results. It is broadly categorized into
two types: static scanning and dynamic scanning. The former scanning technique
involves extracting information of an image without running it into a container,
whereas the latter approach involves launching the container from the target image, and
then scanning the running container.
Here, we focus mainly on vulnerability scanning.
\begin{comment}
Malware is a computer software that is specially designed to attack the target computer,
whereas 
\end{comment}
Vulnerability is a weakness in the developer's software that can be used
by the attacker to perform unathorized actions on the target computer.
In this paper, we report all vulnerabilities that are present in
container images, specifically used by neuroimaging field, and access their
related risks for data analysis. Particularly, we aim to answer three primary
research questions:

@@

\TG{paper suggested by Emad Shihab.}

@@

\subsection{Singularity}

@@

\subsection{Clair Scanner}

@@

\subsection{CBRAIN}

\href{http://github.com/aces/cbrain}{CBRAIN}~\cite{sherif2014cbrain} is a web portal that is
used for the processing of distributed data on various storage locations of computing
clusters. CBRAIN system deployed by Montreal Neurological Institute depends on the infrastructure
delivered by Compute Canada~\cite{das2016mni}.
It is also used by CONP to exploit services of Compute Canada. CBRAIN is a collaborative
neuroimaging research platform that is active in production since 2009. CBRAIN
provides transparent access to various distributed storage sites and computing
resources across the world. CBRAIN’s infrastructure consists of three main
layers, namely access layer, service layer, and infrastructure layer~\cite{sherif2014cbrain}. The access
layer is for CBRAIN users, and can be accessed through any modern browser or
RESTful API. The service layer consists of CBRAIN portal, which contains
metadata and databases. It provides information about users, their permissions,
resources etc. The infrastructure layer consists of data resources and computing
resources, which are connected through a network. 
CBRAIN supports Docker, Singularity, BIDS apps, and Boutiques.
CBRAIN users uses a portal
account on the cluster. Users are only able to
run pre-defined applications on the cluster through the CBRAIN portal.

\section{Results}

@@

Tables show results of scanning BIDS and Boutiques images with above discussed three scanners.
The number of vulnerabilities reported by these scanners are drastically different from each other.
The question arises why these scanners report different number and type of vulnerabilities.
How their logic differs and what exactly is making these results different than each other.
According to our investigation of these results pricisely, below are some of the reasons of
getting different results from these scanners. These reasons include bugs in scanner 's logic,
some scanners ignoring vulnerabilities in a particular package, referring to different databases,
how frequently they are updating their database, etc,. We have explained these differences below in detail
and have provided an example with each reason to make it clear.

\begin{figure}
\csvreader[%
 respect all,%
  before reading=\footnotesize\sisetup{round-mode=places,round-precision=2,round-integer-to-decimal}
      %\caption{Baseline GF Competition Circle Track 2014}\label{tab:baselline1}
      \begin{adjustbox}{max width=\columnwidth},
  after reading=\end{adjustbox},
 tabular={c |c | c | c | c},
        table head =Image & {OS Distro} & {Vulnerabilities by Anchore} & {Vulnerabilities by Clair} & {Vulnerabilities by Vuls}\\\hline,
 late after line= \\,
        late after last line=\\\hline %\multicolumn{5}{c}{Total Score: 1481}
]{results.csv}{}{\csvlinetotablerow}%
       \centering
        \caption{Existing number of Vulnerabilities}
\end{figure}

@@

@@

V-C represents extra vulnerabilities that are shown by Vuls than Clair.
So the next question is why they are not shown by Clair then. 
Below are some reasons to answer that question:
\begin{enumerate}

\item\textbf{With Status as “Not-affected”-} It means these vulnerabilities are affecting Ubuntu but they are not 
affecting particular Ubuntu release that is present inside the image. The reason why its not affecting 
that release is also mentioned. For example, one reason can be that code which is creating issue is not 
present in that release etc. For example CVE-2015-2305 is not affecting package cups in Trusty.

@@

A-C represents extra vulnerabilities shown by Anchore than Clair. Below are the reasons:
\begin{enumerate}
	\item Linux Package: Clair is not detecting all vulnerabilities in the source “Linux” package. 
		For example CVE-2019-9506.
	\item Ignored(reached end-of-life): These vulnerabilities are ignored in Ubuntu 14.04 LTS as it 
		reached end-of-life but does not exist (DNE) in ESM release. As Clair is only referring 
		Ubuntu 14.04 ESM release it do not detect it. For example CVE-2017-994
	\item Database difference: Clair is using a Docker image for database. So it is not updated everyday. 
		When I scanned images I used the latest available container. For example CVE-2019-5094 was not 
		updated in Clair container that time.
	\item False negatives by Clair: Clair is missing vulnerabilities that it should detect. For example 
		CVE-2016-9082 is present in package cairo in Xenial release and it is not detected by Clair
\end{enumerate}

@@

	\item\textbf{EPOCH bug-} There is a bug in the Anchore logic due to which some vulnerabilities are 
		not detected by Anchore. This bug gets triggered when package’s version have epoch 
		(1:3.3.9-1ubuntu2.3)  in it. For example CVE-2018-1125 in procps package
	\item\textbf{Ignored (out of standard support) bug-} There is another bug in Anchore due to 
		which it is not able to detect some vulnerabilities. Due to this bug Anchore does not detect 
		vulnerabilities which have a status as “ignored (out of standard support)” in Ubuntu 14.04 LTS. 
		But if this vulnerability is present in Ubuntu 14.04 ESM release it is detected by Clair. 
		For example CVE-2019-13565 in Ubuntu 14.04
	\item\textbf{Ignored (reached end-of-life)-}Some vulnerabilities have status as “ignored (reached end-of-life)” 
		so Anchore checks the last status of these vulnerabilities whether OS package was vulnerable to the cve 
		prior to the end-of-life. If it was vulnerable only then Anchore will report it, otherwise not. But this 
		vulnerability is present in Ubuntu 14.04 ESM release Clair is reporting that. For example CVE-2019-9924
\end{enumerate}

@@

\subsection{V-A}
V-A represents the vulnerabilities that are detected by Vuls but not detected by Anchore. Below are the reasons:
\begin{enumerate}
\item\textbf{EPOCH bug-} There is a bug in the Anchore logic due to which some vulnerabilities are not detected 
	by Anchore. This bug gets triggered when package’s version have epoch (1:3.3.9-1ubuntu2.3)  in it. 
		For example CVE-2018-1125 in procps package
\item\textbf{Ignored (out of standard support) bug-} There is another bug in Anchore due to which it is not 
	able to detect some vulnerabilities. Due to this bug Anchore does not detect vulnerabilities which 
		have a status as “ignored (out of standard support)” in Ubuntu 14.04 LTS. But these vulnerabilities 
		are detected by Vuls in Ubuntu 14.04 LTS. For example CVE-2019-13565 in Ubuntu 14.04
\item\textbf{With status as “Not-affected”-}  It means these vulnerabilities are affecting Ubuntu but they are not 
	affecting particular Ubuntu release that is present inside the image. The reason why its not affecting that 
		release is also mentioned. For example, one reason can be that code which is creating issue is not 
		present in that release etc. For example CVE-2015-2305 is not affecting package cups in Trusty.
\item\textbf{Rejected CVEs-} There are some CVE that are rejected because they are duplicate copies of another CVEs. 
	So Anchore is not reporting those rejected CVEs but Vuls is reporting those. For example CVE-2017-13753
	\end{enumerate}

@@

The next experiment involves updating all these images and then rescanning them to see how the number of
vulnerabilities drop inside them. We used a \textit{bash} script to update these images. It will find
package manager inside the image and then update the image according the package manager it found.
When these images are rescanned after updation, results changed drastically. However, there are still
vulnerabilities reported by these scanners but there are no fixes available for these vulnerabilities
till date so there is nothing that can be done to remove these vulnerabilties. There are only two
options either you accept those vulnerabilities and use that image, or you discard that image.
So one thing is clear here that even if we keep our images up to date there will be still some
vulnerabilities that we have to face.
Below given table shows number of vulnerabilities that are detected by Anchore after updating these images.

\begin{figure}[!htb]
        {\includegraphics[width=\columnwidth]
        {Figures/afterupdate.png}}
        \caption{\label{fig:graph2} Scatterplot representing difference in number of vulnerabilities before and 
	after update of image}
      \end{figure}
\subsection{Effect Of Size Reduction}

>>>>

Containers, which provide operating system (OS) level virtualization, are very
popular. This is because they are very lightweight, flexible, resource-efficient,
provide fast development cycles, continuous delivery,
and cost reduction of infrastructure. OS-level virtualization gained a lot of interest when Docker was
introduced in 2013~\cite{gantikow2016providing}. However, Docker has security concerns due to which it
is not supported by High Performance
Computing (HPC) environments. As a result, Singularity came in 2016 with the goal of providing support
for HPC environments. It is used in many clusters including Compute Canada.
According to~\cite{kurtzer2017singularity}, Singularity is used in 36 research clusters.

@@

No doubt containers have gained a lot of popularity, however containers tightly
integrate with the host due to the sharing of the kernel, 
mounted file systems, and devices, which raises security
concerns.
They also share three main security threats with other virtualization
techniques~\cite{gantikow2016providing}.

@@

To answer that question, we scan images that are used on Compute
Canada clusters by neuroscience field. Scanning refers to the practice of
collecting all information about the container image, investigating it
for vulnerabilities, and finally producing a
report to summarize scanning results. It is broadly categorized into
two types: static scanning and dynamic scanning. The former scanning technique
involves extracting information of an image without running it into a container,
whereas the latter approach involves launching the container from the target image, and
then scanning the running container.
Here, we focus mainly on vulnerability scanning.
\begin{comment}
Malware is a computer software that is specially designed to attack the target computer,
whereas 
\end{comment}
Vulnerability is a weakness in the developer's software that can be used
by the attacker to perform unathorized actions on the target computer.
In this paper, we report all vulnerabilities that are present in
container images, specifically used by neuroimaging field, and access their
related risks for data analysis. Particularly, we aim to answer three primary
research questions:

@@

@@

\subsubsection{Singularity}

@@

\subsubsection{Clair Scanner}

@@

\begin{comment}
\subsection{CBRAIN}

\href{http://github.com/aces/cbrain}{CBRAIN}~\cite{sherif2014cbrain} is a web portal that is
used for the processing of distributed data on various storage locations of computing
clusters. CBRAIN system deployed by Montreal Neurological Institute depends on the infrastructure
delivered by Compute Canada~\cite{das2016mni}.
It is also used by CONP to exploit services of Compute Canada. CBRAIN is a collaborative
neuroimaging research platform that is active in production since 2009. CBRAIN
provides transparent access to various distributed storage sites and computing
resources across the world. CBRAIN’s infrastructure consists of three main
layers, namely access layer, service layer, and infrastructure layer~\cite{sherif2014cbrain}. The access
layer is for CBRAIN users, and can be accessed through any modern browser or
RESTful API. The service layer consists of CBRAIN portal, which contains
metadata and databases. It provides information about users, their permissions,
resources etc. The infrastructure layer consists of data resources and computing
resources, which are connected through a network. 
CBRAIN supports Docker, Singularity, BIDS apps, and Boutiques.
CBRAIN users uses a portal
account on the cluster. Users are only able to
run pre-defined applications on the cluster through the CBRAIN portal.
\end{comment}
\section{Results}

In this section, we present results of three experiments that are carried out to see
how the number of vulnerabilities vary inside images. First experiment involves scanning
these images as it is to see how vulnerable they are. For scanning we use three different scanners
to see if all are reporting same vulnerabilities or not. Second experiment involves updating
all these images and then rescanning. The last experiment involves shrinking the size of the image
meaning that removing all unnecessary packages from the image to see the effect on the number of
vulnerabilities present inside the image.

@@

Table~\ref{table1} shows results of scanning BIDS and Boutiques images with three scanners namely
Anchore, Clair, and Vuls. These scanners are taking vulnerability feed from different sources. For
example for Ubuntu OS distribution, Anchore refers to Ubuntu launchpad database, Clair refers to
Ubuntu CVE Tracker, whereas Vuls gets data from Open Vulnerability and Assessment Language (OVAL).
The interesting point in the table is that there is no OVAL data for Ubuntu 17.04 and 17.10 distribution,
meaning that images with these distributions are impossible to scan with Vuls. Also, it is interesting to note that
Anchore reports more number of vulnerabilities than Clair and Vuls for all images except that have Centos OS.
Additionally, we notice that Alpine and Centos OS distributions have less number of vulnerabilities as
compared to Ubuntu and Debian.

\begin{table}
\csvreader[%
 respect all,%
  before reading=\footnotesize\sisetup{round-mode=places,round-precision=2,round-integer-to-decimal}
      \begin{adjustbox}{max width=\columnwidth},
  after reading=\end{adjustbox},
 tabular={c |c | c | c | c},
        table head =Image & {OS Distro} & {Vulnerabilities by Anchore} & {Vulnerabilities by Clair} & {Vulnerabilities by Vuls}\\\hline,
 late after line= \\,
        late after last line=\\\hline %\multicolumn{5}{c}{Total Score: 1481}
]{results.csv}{}{\csvlinetotablerow}%
       \centering
	\caption{\label{table1}Existing number of Vulnerabilities}
\end{table}

@@

The number and type of vulnerabilities reported by these scanners are drastically different from each other.
The question arises why these scanners report different number and type of vulnerabilities.
How their logic differs and what exactly is making these results different than each other.
According to our investigation of these results precisely, below are some of the reasons of
getting different results from these scanners. These reasons include bugs in scanner's logic,
some scanners ignoring vulnerabilities in a particular package, referring to different databases,
how frequently they are updating their database, etc,. We have explained these differences below in detail
and have provided an example with each reason to make it clear.

@@

V-C represents extra vulnerabilities that are shown by Vuls than Clair.
So the next question is why they are not shown by Clair then. 
Below are some reasons to answer that question:

\begin{enumerate}

\item\textbf{With Status as “Not-affected”-} It means these vulnerabilities are affecting Ubuntu but they are not 
affecting particular Ubuntu release that is present inside the image. The reason why its not affecting 
that release is also mentioned. For example, one reason can be that code which is creating issue is not 
present in that release etc. In other words, we can say that these are false positives by Vuls.
For example CVE-2015-2305 is not affecting package cups in Trusty.

@@

A-C represents extra vulnerabilities shown by Anchore than Clair. Below are the reasons:
\begin{enumerate}
	\item\textbf{Linux Package-} Clair is not detecting all vulnerabilities in the source “Linux” package. 
		For example CVE-2019-9506.
	\item\textbf{Ignored(reached end-of-life)-} These vulnerabilities are ignored in Ubuntu 14.04 LTS as it 
		reached end-of-life but does not exist (DNE) in ESM release. As Clair is only referring 
		Ubuntu 14.04 ESM release it do not detect it. For example CVE-2017-994.
	\item\textbf{Database difference-} Clair is using a Docker image for database. So it is not updated everyday. 
		When I scanned images I used the latest available container. For example CVE-2019-5094 was not 
		updated in Clair container that time.
	\item\textbf{False negatives by Clair-} Clair is missing vulnerabilities that it should detect. For example 
		CVE-2016-9082 is present in package cairo in Xenial release and it is not detected by Clair.
\end{enumerate}

@@

	\item\textbf{Epoch bug-} There is a bug in the Anchore logic due to which some vulnerabilities are 
		not detected by Anchore. This bug gets triggered when package’s version have epoch 
		(1:3.3.9-1ubuntu2.3)  in it. For example CVE-2018-1125 in procps package.
	\item\textbf{Ignored (out of standard support) bug-} There is another bug in Anchore due to 
		which it is not able to detect some vulnerabilities. Due to this bug Anchore does not detect 
		vulnerabilities which have a status as “ignored (out of standard support)” in Ubuntu 14.04 LTS. 
		But if this vulnerability is present in Ubuntu 14.04 ESM release it is detected by Clair. 
		For example CVE-2019-13565 in Ubuntu 14.04.
	\item\textbf{Ignored (reached end-of-life)-}Some vulnerabilities have status as “ignored (reached end-of-life)” 
		so Anchore checks the last status of these vulnerabilities whether OS package was vulnerable to the cve 
		prior to the end-of-life. If it was vulnerable only then Anchore will report it, otherwise not. But this 
		vulnerability is present in Ubuntu 14.04 ESM release so Clair is reporting that. For example CVE-2019-9924.
\end{enumerate}

@@

\subsection{V-A}
V-A represents the vulnerabilities that are detected by Vuls but not detected by Anchore. Below are the reasons:
\begin{enumerate}
\item\textbf{Epoch bug-} There is a bug in the Anchore logic due to which some vulnerabilities are not detected 
	by Anchore. This bug gets triggered when package’s version have epoch (1:3.3.9-1ubuntu2.3)  in it. 
		For example CVE-2018-1125 in procps package
\item\textbf{Ignored (out of standard support) bug-} There is another bug in Anchore due to which it is not 
	able to detect some vulnerabilities. Due to this bug Anchore does not detect vulnerabilities which 
		have a status as “ignored (out of standard support)” in Ubuntu 14.04 LTS. But these vulnerabilities 
		are detected by Vuls in Ubuntu 14.04 LTS. For example CVE-2019-13565 in Ubuntu 14.04
\item\textbf{With status as “Not-affected”-}  It means these vulnerabilities are affecting Ubuntu but they are not 
	affecting particular Ubuntu release that is present inside the image. The reason why its not affecting that 
		release is also mentioned. For example, one reason can be that code which is creating issue is not 
		present in that release etc. For example CVE-2015-2305 is not affecting package cups in Trusty.
\item\textbf{Rejected CVEs-} There are some CVE that are rejected because they are duplicate copies of another CVEs. 
	So Anchore is not reporting those rejected CVEs but Vuls is reporting those. For example CVE-2017-13753
	\end{enumerate}

@@

The next experiment involves updating all these images and then rescanning them to see how the number of
vulnerabilities drop inside them. We used a \textit{bash} script to update these images. This script is
present in our github repository \href{https://github.com/kaurbhupinder/Risk-to-Clusters-Paper}
{https://github.com/kaurbhupinder/Risk-to-Clusters-Paper}. This script 
will find package manager inside the image and then update the image according the package manager it finds.
When these images are rescanned after updation, results changed drastically. However, there are still
vulnerabilities reported by these scanners but there are no fixes available for these vulnerabilities
till date so there is nothing that can be done to remove these vulnerabilties. There are only two
options, either you accept those vulnerabilities and use that image, or you discard that image.
So one thing is clear here that even if we keep our images up to date there will be still some
vulnerabilities that we have to face.
Figure~\ref{fig:graph2}shows number of vulnerabilities that are detected by Anchore after updating these images.

\begin{figure}[!htb]
        {\includegraphics[width=\columnwidth]
        {Figures/aferupdatewithpackage.png}}
        \caption{\label{fig:graph2} Scatterplot representing difference in number of vulnerabilities before and 
	after update of image}
      \end{figure}
\subsection{Effect Of Size Reduction}
